Ten Simple Rules for Teaching Programming

### 2017-07-09 paper.tex
Adding figure and reference

% FIXME: mention Repenning's boring/exciting X hard/easy framework from "Moving Beyond Syntax" paper.

@@

\begin{figure}\sffamily
\begin{verbatim}
for (int i = 1; i < 10; i++) {
    if (i < 3 || i > 8) {
        System.out.println("Yes");
    }
}
\end{verbatim}
How many times will the above code print out the word Yes?\\
a) 10\\
b) 9\\
c) 4\\
d) 3
\label{fig:mcq}
\caption{An example multiple choice question probing learners' understanding of loops and integer comparisons.}
\end{figure}

@@

\citet{morrison-subgoals,morrison-parsons} have shown that students perform better
when worked examples are broken down into steps (or subgoals)
which are given names (or labels).
Subgoal labels provide a structure which students can apply to future tasks that they attempt themselves,
and allow them to communicate with their peers and instructors more efficiently.
TODO give an example in a figure.

% FIXME give a short code snippet here with some subgoal labels to illustrate - yes please

>>>>

@@

\begin{figure}
\begin{verbatim}
for (int i = 1; i < 10; i++) {
    if (i < 3 || i > 8) {
        System.out.println("Yes");
    }
}
\end{verbatim}
How many times will the above code print out the word Yes?\\
a) 10\\
b) 9\\
c) 4\\
d) 3
\label{fig:mcq}
\caption{An example multiple choice question probing learners' understanding of loops and integer comparisons.}
\end{figure}

@@

\citet{morrison-subgoals,morrison-parsons,margulieux} have shown that students perform better
when worked examples are broken down into steps (or subgoals)
which are given names (or labels) (Figure~\ref{fig:subgoal}).
Subgoal labels provide a structure which students can apply to future tasks that they attempt themselves,
and allow them to communicate with their peers and instructors more efficiently.

\begin{figure}

\noindent
\textbf{Conventional Materials}
\begin{verbatim}
1. Click on "My Blocks" to see the blocks for components you created.
2. Click on "clap"
3. Drag out a when clap.Touched block
4. Click on “clapSound”
5. Drag out call clapSound.Play
6. Connect it after when clap.Touched
\end{verbatim}

\noindent
\textbf{Subgoal Labeled Materials}
\begin{verbatim}
Handle Events from My Blocks

1. Click on "My Blocks" to see the blocks for components you created.
2. Click on "clap"
3. Drag out a when clap.Touched block

Set Output from My Blocks

4. Click on “clapSound” and
5. Drag out call clapSound.Play
6. Connect it after when clap.Touched
\end{verbatim}
\label{fig:subgoal}
\caption{An example of subgoal labeling (taken from \cite{margulieux})}
\end{figure}
